Czech parliament meeting recordings as ASR training data

### 2020-07-02 2020-fedcsis-sofia-svolocz/svolocz.tex
match thesis chapter

The known shortcomings of this method are that 1) it discards the speaker
annotations, although it is valuable metainformation and 2) it skips some short
passages, e.g. references to other meetings, as can be seen in the meeting
from Feb. 12th 2020 10:10 -
10:20\footnote{https://www.psp.cz/eknih/2017ps/stenprot/040schuz/s040372.htm}.

@@

@@

I have used the Perl module \texttt{Lingua::CS::Num2Word} as a base for the
expansion. I modified the module in the following way: 1) I added support
the order of billions, which is very common in the corpus. 2) A number is no
longer expanded into a single phrase but instead into all possible phrases
expressing the given number. 3) I added support for genitive and accusative
cases, decimal numerals, ordinals, dates and times.

@@

Common abbreviations and symbols are expanded together with the digits. For
example, the very common character \textit{``§'' (paragraph)} is expanded into
the forms \textit{paragraf, paragrafu, paragrafů, paragrafem,
paragrafech} that represent common inflections of the word. Some common
abbreviations that undergo inflection include \textit{``čl.'' (article)},
\textit{``odst.''}, which also means ``paragraph'' and \textit{``tzv.''
(co-called)}.

With the expansion in the process, the similarity of the stenographic transcript
and the initial one raised, which raised the number of accepted segments from
26\% to 35\%. The amount of training data grew by 86 hours to 1144.

@@

I have trained a standard DeepSpeech\cite{hannun2014deep} model on the 1058
hours with training :
development : test ratio of 18 : 1 : 1; batch size 50; learning rate 0.0001; dropout
rate 0.2. The training took 12 epochs to reach optimal dev fit and the final
word error rate on testing data from the corpus itself is 8.40\%.

@@

\begin{table}[htpb]
\caption{Word error rate of speech recognition on the individual corpora and on
their concatenation.}
\centering
\begin{tabular}{|l||r|r|}
\hline
source    & WER on self & WER on all \\
\hline
bible     & 9.20\%  & 94.7\% \\
cucfn     & 31.6\%  & 72.8\% \\
makon     & 30.4\%  & 77.3\% \\
oral2013  & 78.4\%  & 60.7\% \\
ovm       & 21.6\%  & 72.9\% \\
\textbf{parliament}
          & 8.74\%  & \textbf{39.7\%} \\
vystadial & 51.0\%  & 74.0\% \\
\hline
all       & 28.4\%  & 28.4\% \\
\hline
\end{tabular}
\label{tab:csasr:results}
\end{table}

All speech recognition systems were trained with the same hyperparameters as
described above. For a fairer comparison, a common, general language model was
used for all the tests. Hence the higher WER for the Parliament corpus tested on
itself than the reported 8.40\%.

>>>>

The known shortcomings of this method are that 1) it discards the speaker
annotations, although it is valuable metainformation and 2) it skips some short
passages, e.g. references to other meetings, as can be seen in the meeting
from Feb. 12th 2020 10:10 -
10:20\footnote{https://www.psp.cz/eknih/2017ps/stenprot/040schuz/s040372.htm}.
Both can be corrected by devising a smarter scraper and neither has any
significance for speech recognition: speaker annotation fundamentally and
neglecting the links for their infrequency.

@@

Nota bene, a GMM-based system was chosen for the initial transcript instead of
a DNN-based for three reasons: 1) Foremost, it is straightforward to obtain
precise alignment from a GMM-based system. 2) The training doesn't require so
much computational resources and data. 3) It isn't crucial to have maximum possible
accuracy in this stage.

@@

I have used the Perl module \texttt{Lingua::CS::Num2Word} as a base for the
expansion. I modified the module in the following way: 1) I added support for
the order of billions, which is very common in the corpus. 2) A number is no
longer expanded into a single phrase but instead into all possible phrases
expressing the given number. 3) I added support for genitive and accusative
cases, decimal numerals, ordinals, dates and times.

@@

Common abbreviations and symbols are expanded together with the digits. For
example, the very common character \textit{``§'' (paragraph)} is expanded into
the forms \textit{paragraf, paragrafu, paragrafů, paragrafem,
paragrafech} that represent common inflections of the word. Some common
abbreviations that undergo inflection include \textit{``čl.'' (article)},
\textit{``odst.'' (also paragraph)} and \textit{``tzv.'' (co-called)}.

After incorporating the expansion into the pipeline, the similarity of the
stenographic transcript and the initial one raised, which also raised the number
of accepted segments from 26\% to 35\%. The amount of training data grew by 86
hours to 1144.

@@

I have trained a standard DeepSpeech\cite{hannun2014deep} model on the 1058
hours with training :
development : test ratio of 18 : 1 : 1; batch size 50; learning rate 0.0001; dropout
rate 0.2. The training took 12 epochs to reach optimal dev fit and the final
word error rate on testing data from the corpus itself is 8.40\% before digit
expansion and 7.89\% afterwards.

@@

\begin{table}[htpb]
\caption{Word error rate of speech recognition on the individual corpora and on
their concatenation.}
\centering
\begin{tabular}{|l||r|r|}
\hline
source    & WER on self & WER on all \\
\hline
bible     & 9.20\%  & 94.7\% \\
cucfn     & 31.6\%  & 72.8\% \\
makon     & 30.4\%  & 77.3\% \\
oral2013  & 78.4\%  & 60.7\% \\
ovm       & 21.6\%  & 72.9\% \\
parliament w/digits
          & 8.74\%  & 39.7\% \\
\textbf{parliament expanded}
          & 7.89\%  & \textbf{36.0\%} \\
vystadial & 51.0\%  & 74.0\% \\
\hline
all       & 28.4\%  & 28.4\% \\
\hline
\end{tabular}
\label{tab:csasr:results}
\end{table}

All speech recognition systems were trained with the same hyperparameters as
described above.% For a fairer comparison, a common, general language model was
%used for all the tests. Hence the higher WER for the Parliament corpus tested on
%itself than the reported 8.40\%.
